Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-04-03 pkg/disttree/inst/draft/draft.Rnw
now calling function evalmodels instead of eval
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2121 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 70b7de01b854ba21101f6cbf01857c84866fcb2c

                            res <- eval(station = "Axams",
                                        train = train,
                                        test = test,
                                        gamboost_cvr = TRUE)

@@

                              res <- eval(station = stations[i],
                                          train = train,
                                          test = test,
                                          gamboost_cvr = TRUE)

>>>>

                            res <- evalmodels(station = "Axams",
                                              train = train,
                                              test = test,
                                              gamboost_cvr = TRUE)

@@

                              res <- evalmodels(station = stations[i],
                                                train = train,
                                                test = test,
                                                gamboost_cvr = TRUE)
